---
title: "R Notebook"
output: html_notebook
---
```{r}
library(corrplot)
library(tidyverse)
library(reticulate)
```

```{r}
houses <- read.csv(file = 'data/paris.csv')
```

```{r}
dim(houses)
head(houses)
```

```{r}
summary(houses)
```

```{r}
mcor <- cor(houses)
```

```{r}
corrplot(mcor, type="upper", order="hclust", tl.col="black", tl.srt=45)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{python}
from sklearn.model_selection import train_test_split
houses = houses.drop('cityCode', axis = 1)
train_set, test_set = train_test_split(houses, test_size = 0.2, random_state = 42)
print(train_set.shape, test_set.shape)
```

